Optimal Parameter Selection in Markov State Models for Biomolecular Conformational Dynamics

### 2013-08-15 paper/paper2.tex
abstract

\begin{abstract}
Likelihood framework for choosing the optimal number of states in a
Markov State Model
\end{abstract}

>>>>

\begin{abstract}
Markov state models (MSMs) are a powerful tool for the analysis of molecular dynamics simulations, but have been hampered by the need for manual selection of the number of states. We report a new method for the optimal selection of the number of states in an MSM based on the Bayesian information criterion. We demonstrate the approach on three systems of increasing complexity...
\end{abstract}
